An Embedding Framework for Consistent Polyhedral Surrogates

### 2019-05-23 neurips-19/poly-embed.tex
minor

\subsection{Related works}
\raf{Let's dump a bunch of citations and not worry about going into detail.  I'll throw in a skeleton.}

The literature on convex surrogates focuses mainly on smooth surrogate losses~\raf{DKR;many more...}\jessiet{DKR, some of Bob's added.}\cite{crammer2001algorithmic,bartlett2006convexity,bartlett2008classification, duchi2018multiclass, williamson2016composite, reid2010composite}.
Nevertheless, nonsmooth losses, such as the polyhedral losses we consider, have been proposed and studied for a variety of classification-like problems\cite{ramaswamy2018consistent, boser1992training}\raf{cites} \jessiet{Do we want the SVM (Boser) cite?}.
A notable addition to this literature is~\citet{ramaswamy2018consistent}, who argue that nonsmooth losses may enable dimension reduction of the prediction space (range of the surrogate hypothesis) relative to smooth losses, illustrating this conjecture with a surrogate for \emph{abstain loss} needing only $\log n$ dimensions for $n$ labels, whereas the best known smooth loss needs $n-1$.
Their surrogate is a natural example of an embedding (cf.~Section~\ref{sec:abstain}), and serves as inspiration for our work.

>>>>

\subsection{Related works}

The literature on convex surrogates focuses mainly on smooth surrogate losses~\cite{crammer2001algorithmic,bartlett2006convexity,bartlett2008classification, duchi2018multiclass, williamson2016composite, reid2010composite}.
Nevertheless, nonsmooth losses, such as the polyhedral losses we consider, have been proposed and studied for a variety of classification-like problems\cite{ramaswamy2018consistent, boser1992training}\raf{cites} \jessiet{Do we want the SVM (Boser) cite?}.
A notable addition to this literature is~\citet{ramaswamy2018consistent}, who argue that nonsmooth losses may enable dimension reduction of the prediction space (range of the surrogate hypothesis) relative to smooth losses, illustrating this conjecture with a surrogate for \emph{abstain loss} needing only $\log n$ dimensions for $n$ labels, whereas the best known smooth loss needs $n-1$.
Their surrogate is a natural example of an embedding (cf.~Section~\ref{sec:abstain}), and serves as inspiration for our work.
